### 2014-01-22 paper_draft.tex
edited according to PLOS publishing guidelines for final proof

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\long\def\authornote#1{%
        \leavevmode\unskip\raisebox{-3.5pt}{\rlap{$\scriptstyle\diamond$}}%
        \marginpar{\raggedright\hbadness=10000
        \def\baselinestretch{0.8}\tiny
        \it #1\par}}
\newcommand{\bastian}[1]{\authornote{BG: #1}}
\newcommand{\fabian}[1]{\authornote{FZ: #1}}
\newcommand{\philipp}[1]{\authornote{PB: #1}}
%% END MACROS SECTION
\begin{document}

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - a crowdsourced web resource for personal genomics}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,2,\ast}$, 
Philipp E. Bayer$^{3,4}$, 
Helge Rausch$^{5}$,
Julia Reda$^{6}$
\\
\bf{1} Molecular Ecology Group, Goethe University Frankfurt am Main, Germany
\\
\bf{2} Department for Applied Bioinformatics, Institute for Cell Biology and Neuroscience, Goethe University Frankfurt am Main, Germany 
\\
\bf{3} School of Land, Crop and Food Sciences and Australian Centre for Plant Functional Genomics, University of Queensland, Brisbane, Australia
\\
\bf{4} Australian Centre for Plant Functional Genomics, School of Agriculture and Food Sciences, University of Queensland, Brisbane, Australia
\\
\bf{5} Hochschule f\"ur Technik und Wirtschaft Berlin, Germany 
\\
\bf{6} Johannes Gutenberg University Mainz, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

@@

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step.
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}

@@

\section*{Tables}
\begin{table}
\caption{Comparison of crowdsourced genetics platforms. N/A = Not Applicable, \checkmark = Present, \xmark = Absent *SNPedia only provides an API to webpages of individual SNPs, not access to genetic data of individuals}
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
Name & Provides  & Provides & Open  & API & IRB approval & License \\ 
& annotation & data & enrollment & & & \\
\hline
SNPedia & (\checkmark*) & \xmark & N/A & \checkmark & N/A & CC-NC-SA 3.0 \\ 
\hline
PGP & \checkmark & \checkmark & \xmark & \xmark & \checkmark & CC-BY 1.0, CC0 \\
\hline
PatientsLikeMe & \xmark & \checkmark & \checkmark & \xmark & \checkmark & Closed, CC-BY-SA 3.0 \\
\hline
openSNP & \checkmark & \checkmark & \checkmark & \checkmark & \xmark & CC-BY 3.0 \\
\hline
\end{tabular}
\label{tab:platforms}
\end{table}
%\begin{table}
%\caption{Differences in terms of motivation to share genotypings with the public in survey-participants who already received a genotyping compared to participants who are not planning to getting genotyped. }  
%\begin{tabular}{|p{7cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
%\hline
%& Mean \emph{Genotyped} & Mean \emph{Not Genotyped} & Mean Difference & Standard Error\\ 
%\hline
%\textbf{Motivation for sharing data in participants who are already genotyped} & & & & \\
%\hline 
%... curious & 3.82 & 2.66 & 1.159 & 0.193 \\ \hline % checked
%... want to help scientists & 4.64 & 4.18  & 0.465 & 0.128 \\ \hline % checked
%... for personal benefits & 3.77 & 3.32  & 0.448 & 0.183 \\ \hline % checked
%\textbf{Motivation for not sharing in participants who are not planning to get genotyped} & & & & \\ \hline
%... fear of discrimination & 3.09 & 4.15  & 1.06 & 0.195 \\ \hline % checked
%... breach of privacy & 3.01 & 3.68  & 0.666 & 0.211 \\ \hline % checked
%... fear of personalized advertising & 3.03 & 3.88  & 0.848 & 0.208 \\ \hline % checked
%... negative consequences for family members & 2.93 & 3.57  & 0.639 & 0.197 \\ \hline 
%\end{tabular}
%\label{tab:motivations1}
%\end{table}
%
%\begin{table}
%\caption{Differences in terms of motivations to share genotyping-data, comparison between participants who would share their genotyping data with participants who would not share their data.}
%\begin{tabular}{|p{7cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
%\hline
%& Mean {Sharing} & Mean {Not Sharing} & Mean Difference & Standard Error \\ 
%\hline
%\textbf{Motivation for sharing genotypings in participants who would share} & & & & \\
%\hline
%... curiosity & 3.86 & 1.87 & 1.99 & 0.321 \\ \hline % checked
%... want to help science & 4.70 & 3.13 & 1.57 & 0.199 \\ \hline % checked
%... for personal benefits & 3.68 & 2.73 & 0.951 & 0.308 \\ \hline % checked
%\textbf{Motivation for sharing genotypings in participants who would not share} & & & & \\
%\hline
%... fear of discrimination & 3.21 & 4.73 & 1.52 & 0.322 \\ \hline % checked
%... fear of consequences for family members & 2.79 & 3.93 & 1.146 & 0.32 \\ \hline % checked
%... fear of personalized advertising & 3.17 & 4.29 & 1.112 & 0.357 \\ \hline % checked
%\end{tabular}
%\label{tab:motivations2}
%\end{table}
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

>>>>

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\long\def\authornote#1{%
        \leavevmode\unskip\raisebox{-3.5pt}{\rlap{$\scriptstyle\diamond$}}%
        \marginpar{\raggedright\hbadness=10000
        \def\baselinestretch{0.8}\tiny
        \it #1\par}}
\newcommand{\bastian}[1]{\authornote{BG: #1}}
\newcommand{\fabian}[1]{\authornote{FZ: #1}}
\newcommand{\philipp}[1]{\authornote{PB: #1}}
\usepackage[utf8x]{inputenc}
\DeclareUnicodeCharacter{2717}{✗}
%\usepackage{newunicodechar}
%\newunicodechar{✓}{\checkmark}
%\newunicodechar{✘}{\xmark}

%% END MACROS SECTION
\begin{document}

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - a crowdsourced web resource for personal genomics}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,2,\ast}$, 
Philipp E. Bayer$^{3,4}$, 
Helge Rausch$^{5}$,
Julia Reda$^{6}$
\\
\bf{1} Molecular Ecology Group, Biodiversity \& Climate Research Centre, Frankfurt am Main, Germany
\\
\bf{2} Department for Applied Bioinformatics, Institute for Cell Biology and Neuroscience, Goethe University, Frankfurt am Main, Germany 
\\
\bf{3} School of Land, Crop and Food Sciences and Australian Centre for Plant Functional Genomics, University of Queensland, Brisbane, Australia
\\
\bf{4} Australian Centre for Plant Functional Genomics, School of Agriculture and Food Sciences, University of Queensland, Brisbane, Australia
\\
\bf{5} Hochschule f\"ur Technik und Wirtschaft, Berlin, Germany 
\\
\bf{6} Johannes Gutenberg University, Mainz, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

@@

@@

\section*{Tables}
\begin{table}
\caption{Comparison of crowdsourced genetics platforms. N/A = Not Applicable, x = Present, - = Absent *SNPedia only provides an API to webpages of individual SNPs, not access to genetic data of individuals}
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
Name & Provides  & Provides & Open  & API & IRB approval & License \\ 
& annotation & data & enrollment & & & \\
\hline
SNPedia & (x*) & - & N/A & x & N/A & CC-NC-SA 3.0 \\ 
\hline
PGP & x & x & - & - & x & CC-BY 1.0, CC0 \\
\hline
PatientsLikeMe & - & x & x & - & x & Closed, CC-BY-SA 3.0 \\
\hline
openSNP & x & x & x & x & - & CC-BY 3.0 \\
\hline
\end{tabular}
\label{tab:platforms}
\end{table}
%\begin{table}
%\caption{Differences in terms of motivation to share genotypings with the public in survey-participants who already received a genotyping compared to participants who are not planning to getting genotyped. }  
%\begin{tabular}{|p{7cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
%\hline
%& Mean \emph{Genotyped} & Mean \emph{Not Genotyped} & Mean Difference & Standard Error\\ 
%\hline
%\textbf{Motivation for sharing data in participants who are already genotyped} & & & & \\
%\hline 
%... curious & 3.82 & 2.66 & 1.159 & 0.193 \\ \hline % checked
%... want to help scientists & 4.64 & 4.18  & 0.465 & 0.128 \\ \hline % checked
%... for personal benefits & 3.77 & 3.32  & 0.448 & 0.183 \\ \hline % checked
%\textbf{Motivation for not sharing in participants who are not planning to get genotyped} & & & & \\ \hline
%... fear of discrimination & 3.09 & 4.15  & 1.06 & 0.195 \\ \hline % checked
%... breach of privacy & 3.01 & 3.68  & 0.666 & 0.211 \\ \hline % checked
%... fear of personalized advertising & 3.03 & 3.88  & 0.848 & 0.208 \\ \hline % checked
%... negative consequences for family members & 2.93 & 3.57  & 0.639 & 0.197 \\ \hline 
%\end{tabular}
%\label{tab:motivations1}
%\end{table}
%
%\begin{table}
%\caption{Differences in terms of motivations to share genotyping-data, comparison between participants who would share their genotyping data with participants who would not share their data.}
%\begin{tabular}{|p{7cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
%\hline
%& Mean {Sharing} & Mean {Not Sharing} & Mean Difference & Standard Error \\ 
%\hline
%\textbf{Motivation for sharing genotypings in participants who would share} & & & & \\
%\hline
%... curiosity & 3.86 & 1.87 & 1.99 & 0.321 \\ \hline % checked
%... want to help science & 4.70 & 3.13 & 1.57 & 0.199 \\ \hline % checked
%... for personal benefits & 3.68 & 2.73 & 0.951 & 0.308 \\ \hline % checked
%\textbf{Motivation for sharing genotypings in participants who would not share} & & & & \\
%\hline
%... fear of discrimination & 3.21 & 4.73 & 1.52 & 0.322 \\ \hline % checked
%... fear of consequences for family members & 2.79 & 3.93 & 1.146 & 0.32 \\ \hline % checked
%... fear of personalized advertising & 3.17 & 4.29 & 1.112 & 0.357 \\ \hline % checked
%\end{tabular}
%\label{tab:motivations2}
%\end{table}
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}
